A holomorphic approach to membranes and fivebranes

### 2022-07-19 fivebranes/intro.tex
macros

A more concrete, albeit informal, statement is as follows. Let $X$ be a smooth manifold, and let $\Obs_{grav}$ denote a factorization algebra on $X$ that we view as the observables of some bulk gravitational theory. Suppose we in addition have a stack of $N$ branes, wrapping a submanifold $\iota: Y\into X$, whose worldvolume theory has a factorization algebra of observables $\Obs^{N}_{brane}$.

\begin{}[Twisted Holographic Principle]
  There is a map of factorization algebras
  \[
        (\iota^{*}\Obs_{grav})^{!}\to \Obs^{N}_{brane}
  \]

      that becomes an equivalence in the large $N$ limit.
    \end{}

>>>>

A more concrete, albeit informal, statement is as follows. Let $X$ be a smooth manifold, and let $\Obs_{grav}$ denote a factorization algebra on $X$ that we view as the observables of some bulk gravitational theory. Suppose we in addition have a stack of $N$ branes, wrapping a submanifold $\iota: Y\to X$, whose worldvolume theory has a factorization algebra of observables $\Obs^{N}_{brane}$.

\begin{slogan}[Twisted Holographic Principle]
  There is a map of factorization algebras
  \[
        (\iota^{*}\Obs_{grav})^{!}\to \Obs^{N}_{brane}
  \]

      that becomes an equivalence in the large $N$ limit.
\end{slogan}
